ms_4

### 2020-03-07 ms_4.Rmd
drug deaths over time

---
title: "ms_3"
author: "Suruchi Ramanujan"
date: "2/27/2020"
output: html_document
---

@@

# This data tracks the spending over a course of five years of a series of
# drugs. I want to compare the spending levels of the different kinds of drugs
# by categorizing them based on their use. Perhaps, we will find a correlation
# between spending and drug type for opioid deaths.

@@

Data set 1: Data Set Tracks Overall trends in drug spending amongst opioids and nonopioids across the country. I want to look at this just to see which types of drugs are receiving the most attention and is it with reason that these drugs are being spent on.

Data set 2: Data Set 2 introduces the audience to opioid deaths by county in New York from 2003- 2017. I imagine using a heat map to see how levels have changed over time/ whether there is a trend in opioid deaths.

Data set 3: Data Set 3 outlines the spending in New York on one of the worst addiction drugs (Cocaine) vs. three of the most widely used addiction treatment drugs (Methadone, Naloxone, and Buprenorphine). This site has information for other drugs too so I may include those as well. I still have to decide which drugs to include though.

@@

Data sources:For Data sets 1 and 2, I used healthdata.gov. For Data sets 3 and 4, I used Data Commons.

>>>>

---
title: "ms_4"
author: "Suruchi Ramanujan"
date: "3/6/2020"
output: html_document
---
---
title: "ms_4"
author: "Suruchi Ramanujan"
date: "3/6/2020"
output: html_document
---
** This is a modified version of ms_3 since I answered many of the questions for ms_4 in last week's analysis.*

@@

These first ___ are the new data sets
```{r}
# This data provides state-specific numbers regarding the number of drug
# overdose deaths per state as well as the predicted numbers for drug overdose
# deaths. I am super excited to plot this graph onto a map and look at how the
# worst affected states change over time. I am also interested in seeing whether
# trends match across drug groups.

drugoverdosedeaths<- read.csv("VSRR_Provisional_Drug_Overdose_Death_Counts.csv") %>%
  clean_names() %>%
  select("state", "year", "month", "indicator", "data_value", "state_name", "predicted_value")
```

```{r}
# This data tracks the spending over a course of five years of a series of
# drugs. I want to compare the spending levels of the different kinds of drugs
# by categorizing them based on their use. Perhaps, we will find a correlation
# between spending and drug type for opioid deaths.

@@

Data Set 1: Data Set Tracks Overall trends in drug spending amongst opioids and nonopioids across the country. I want to look at this just to see which types of drugs are receiving the most attention and is it with reason that these drugs are being spent on.

Data Set 2: Data Set 2 introduces the audience to opioid deaths by county in New York from 2003- 2017. I imagine using a heat map to see how levels have changed over time/ whether there is a trend in opioid deaths.

Data Set 3: Data Set 3 outlines the spending in New York on one of the worst addiction drugs (Cocaine) vs. three of the most widely used addiction treatment drugs (Methadone, Naloxone, and Buprenorphine). This site has information for other drugs too so I may include those as well. I still have to decide which drugs to include though.

@@

Data sources:For Data Sets 1 and 2, I used healthdata.gov. For Data Sets 3 and 4, I used Data Commons.

Future: I think I am content with the state specific data with drugs of choice but I think it would be cool to also map out opioid deaths based on country region or based on income levels in a location. I still have to flesh out this idea though.
